### 2019-09-18 README.Rmd
Spelling edits and typos in figure legends for README and vignette

cap <- c("Figure 1. diffEnrich Analysis pipeline. Functions within the diffEnrich package are represented by blue rectangles. The data that must be provided by the user is represented by the pruple ovals. Data objects generated by a function in diffEnrich are representaed by red ovals. The external call of the get_kegg function to the KEGG REST API is represented in yellow.")
```

>>>>

cap <- c("Figure 1. diffEnrich Analysis pipeline. Functions within the diffEnrich package are represented by blue rectangles. The data that must be provided by the user is represented by the purple ovals. Data objects generated by a function in diffEnrich are represented by red ovals. The external call of the get_kegg function to the KEGG REST API is represented in yellow.")
```
